### 2013-07-31 5/applications.tex
Final changes before submission to Alan???

In this chapter, some beneficial applications of the proposed models are presented,
  which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
filtering.
This chapter also shows how the MSE can then be 
applicable in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
 POLSAR speckle filters.

@@

\lstset{language=Matlab,caption=Homogeneous partitions number growing,label=lst:k_mle_algo_partition_number}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
\begin{lstlisting}[frame=tb]
function centers = partition_into_homogenous_groups(l, threshold)
  c_init = maximum_likelihood_of(l);
  [further_partition_needed, c_new] = 
          check_homogeneity_status(l, c_init, threshold);

@@

%\section{Experiment Results and Discussions}%describe analysis and compare
\subsection{Evaluating the k-MLE algorithm}
\label{sec:k_mle_result}

@@

Figure \ref{fig:k_mle_diff_threshold} shows various degrees of speckle filtering controllable by using different threshold-values.
Using the same moving window size of $3\times3$, the effect of filtering is clearly proportional to the threshold values employed.
This can be observed from Figs. \ref{fig:k_mle_threshold_original} to \ref{fig:boxcar_filter}
where the  visual quality  reflects the effects of the kMLE speckle filter when its  
threshold is set at 0\% (i.e. left untouched), 25\%, 80\% and 100\% (i.e. equals to the boxcar filter) respectively.

@@

Another way to improve the raw k-MLE speckle filter is to apply it iteratively.
As can be seen in Fig. \ref{fig:k_mle_diff_threshold}, a normal $3\times3$ k-MLE filter would not filter as much noise as a $3\times3$ boxcar filter. 
At the same time, a $5\times5$ boxcar filter, while having better speckle suppression power, would lose out by its blurring effects as can be seen in Fig. \ref{fig:boxcar_5x5}. 
To improve k-MLE filtering power while avoiding the blurring effect, the k-MLE speckle filter can be used iteratively. 
Presented in the figure \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a $3\times3$ window with 25\% threshold-value, being applied iteratively for four times. 
From the plot, the $3\times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5\times5$ boxcar filter,
  while its visual imagery output appears much sharper, qualitatively speaking.

@@

The k-MLE filters are also applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
Figure \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
It is obvious that the k-MLE speckle filter delivers a significantly ``better'' image than the original data.

@@

\subsection{The F-MLE SAR Speckle Filters}

@@

\begin{figure}[h!]
\begin{minipage}[c]{0.48\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{figure}
%\centering
	\subfloat[Point Target]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/641bcaad-f54b-4bb6-8d10-77784da522a5.made.eps} 
		 \label{fig:point_target_pattern}
	}
	\subfloat[Edge]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/c5124949-1228-4749-a99e-caf9430e400a.made.eps} 
		 \label{fig:edge_pattern}
	}\\
	\subfloat[Line]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/a2e330a8-3deb-4328-94d8-d18c43e4f7a1.made.eps} 
		 \label{fig:line_pattern}
	}
	\subfloat[Dotted Pattern]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/38e79d4c-af61-4b1f-acc2-528ecedb96a7.made.eps} 
		 \label{fig:dotted_pattern}
	}
%\caption{Simulated Heterogeneous Patterns}
%\label{fig:distance_pdf_simulation_iterative}
%\end{figure}
\end{minipage}
%} & 
\begin{minipage}[c]{0.4\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{table}
%\centering
  \footnotesize
\begin{tabular}{|l|l|l|l|}
\hline
Scene 				& Filter 						& MSE 	& AUC \\
\hline
Point Target 	& F-MLE (incl, 3x3) 	& 1.38	& 0.901 \\
Point Target 	& F-MLE (excl, 3x3) 	& 1.47	& 0.893 \\
Point Target 	& boxcar (3x3) 			& 1.56	& 0.826 \\
Point Target 	& boxcar (5x5) 			& 2.67	& 0.502 \\
\hline
Edge 	& F-MLE (incl, 3x3) 	& 0.68	& 0.969 \\
Edge 	& F-MLE (excl, 3x3) 	& 0.73	& 0.964 \\
Edge 	& boxcar (3x3) 			& 1.03	& 0.942 \\
Edge 	& boxcar (5x5) 			& 1.51	& 0.934 \\
\hline
Line 	& F-MLE (incl, 3x3) 	& 1.89	& 0.791 \\
Line 	& F-MLE (excl, 3x3) 	& 2.02	& 0.767 \\
Line 	& boxcar (3x3) 			& 2.27	& 0.658 \\
Line 	& boxcar (5x5) 			& 2.88	& 0.375 \\
\hline
Dotted 			& F-MLE (incl, 3x3) 	& 2.28	& 0.639 \\
Dotted 			& F-MLE (excl, 3x3) 	& 2.32	& 0.621 \\
Dotted 			& boxcar (3x3) 			& 2.92	& 0.431 \\
Dotted 			& boxcar (5x5) 			& 3.35	& 0.382 \\
\hline
\end{tabular}
%\caption{The MSE \& ROC indices are correlated}
%\end{table}
\end{minipage}
%}
%\end{tabular}
\caption{Heterogeneous Patterns: MSE criteria and F-MLE performance}
\label{fig:Heterogeneous_Patterns}
\end{figure}

@@

The log-transformed domain provides a consistent sense of distance. By embracing
a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes
use of this consistency. Experimental results suggest that the estimatorâ output also
exhibits this consistency property, which allows recursive application of the filter discussed above.

@@

\begin{figure}[h]
 \centering
 \epsfxsize=2.4in
 \epsfysize=1.2in
 \epsffile{images/simulation_schema.eps} 	
\caption{SAR simulation, processing and filtering schema}
\label{fig:simul_process_filter_schema}
\end{figure}
%***IVM: Can you make the text bigger, or just increase the figure size? A width of about 12cm would probably be OK.

@@

Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
evaluated by examining the separability of the two background and target populations.
Figures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
	allows visual evaluation of target and clutter histograms and their separability.
Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
in subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
respectively, and is measured by computing the Area Under these Curves (AUC).

@@

Detailed examination of figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
	can help to explain how the MSE is related to the histograms' separation capability.
In pre-filtered images, shown in figures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
\ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
Then the separability of background and target populations depends only on the variance of the additive noise. 
This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) of these sample histograms, 
the better the separation capability.

In post-filtered images, shown in figures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
\ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
A closer examination of Fig. \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
also introduce bias errors.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are 
always over-estimated. This is probably due to the entropy reduction effect of the speckle filters.
Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
Pattern  & AUC - $MSE_{true}$  & AUC - $MSE_{benchmark}$  \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

@@

In the case of partial POLSAR, d=2, then
\begin{align*}
&  var_2 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1)     = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 &\\
\noindent \text{Similar to the SAR case: } \\
&  1/L + 1/(L-1) < var_2 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) & \\
\noindent \text{Thus, approximately: } \\
& var_2 \left[ \ln |C_v| \right] = 2/(L-1) & \\
\noindent \text{Equivalently: } \\
& L = 2/var_2 \left[ \ln |C_v| \right] + 1 & \\
\end{align*}
%Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
%Thus an approximation can be made: $var_d \left[ \ln |C_v| \right] = 2/(L-1)$.
%Equivalently L can be estimated as:  $L = 2/var_d \left[ \ln |C_v| \right] + 1$

In the case of full POLSAR, d=3, then
\begin{align*}
&  var_3 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2)    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 & \\
\noindent \text{Again: }  \\
& 1/L + 1/(L-1) + 1/(L-2) < var_3 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3) &\\
\noindent \text{With } L>3 \\
& var_3 \left[ \ln |C_v| \right] = 3/(L-1.5) &\\
\noindent \text{Or: }\\
& L = 3/var_3 \left[ \ln |C_v| \right] + 1.5 &
\end{align*}
%Again, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
%With $L>3$, it is trivial to prove that $3/(L-1.5)$ is also bounded by the same limits. %also is bounded by the above thresholds.
%Thus a similar approximation can be written as: $var_d \left[ \ln |C_v| \right] = 3/(L-1.5)$
%or $L = 3/var_d \left[ \ln |C_v| \right] + 1.5$

>>>>

In this chapter, some beneficial applications of the proposed models are presented,
  which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
filtering.
This chapter also shows how the MSE can then be 
applied in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
 POLSAR speckle filters.

@@

{\small
\lstset{language=Matlab,caption=Homogeneous partitions number growing,label=lst:k_mle_algo_partition_number}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
\begin{lstlisting}[frame=tb]
function centers = partition_into_homogenous_groups(l, threshold)
  c_init = maximum_likelihood_of(l);
  [further_partition_needed, c_new] = 
          check_homogeneity_status(l, c_init, threshold);

@@

%\section{Experiment Results and Discussions}%describe analysis and compare
\subsection{Evaluating the k-MLE algorithm}
\label{sec:k_mle_result}
}%

@@

Fig. \ref{fig:k_mle_diff_threshold} shows various degrees of speckle filtering controllable by using different threshold-values.
Using the same moving window size of $3\times3$, the effect of filtering is clearly proportional to the threshold values employed.
This can be observed from Figs. \ref{fig:k_mle_threshold_original} to \ref{fig:boxcar_filter}
where the  visual quality  reflects the effects of the kMLE speckle filter when its  
threshold is set at 0\% (i.e. left untouched), 25\%, 80\% and 100\% (i.e. equals to the boxcar filter) respectively.

@@

Another way to improve the raw k-MLE speckle filter is to apply it iteratively.
As can be seen in Fig. \ref{fig:k_mle_diff_threshold}, a normal $3\times3$ k-MLE filter would not filter as much noise as a $3\times3$ boxcar filter. 
At the same time, a $5\times5$ boxcar filter, while having better speckle suppression power, would lose out by its blurring effects as can be seen in Fig. \ref{fig:boxcar_5x5}. 
To improve k-MLE filtering power while avoiding the blurring effect, the k-MLE speckle filter can be used iteratively. 
Presented in the Fig. \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a $3\times3$ window with 25\% threshold-value, being applied iteratively for four times. 
From the plot, the $3\times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5\times5$ boxcar filter,
  while its visual imagery output appears much sharper, qualitatively speaking.

@@

The k-MLE filters are also applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
Fig. \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
It is obvious that the k-MLE speckle filter delivers a significantly ``better'' image than the original data.

@@

\subsection{The f-MLE SAR Speckle Filters}

@@

\begin{figure}[h!]
\begin{minipage}[c]{0.48\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{figure}
%\centering
	\subfloat[Point Target]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/641bcaad-f54b-4bb6-8d10-77784da522a5.made.eps} 
		 \label{fig:point_target_pattern}
	}
	\subfloat[Edge]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/c5124949-1228-4749-a99e-caf9430e400a.made.eps} 
		 \label{fig:edge_pattern}
	}\\
	\subfloat[Line]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/a2e330a8-3deb-4328-94d8-d18c43e4f7a1.made.eps} 
		 \label{fig:line_pattern}
	}
	\subfloat[Dotted Pattern]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/38e79d4c-af61-4b1f-acc2-528ecedb96a7.made.eps} 
		 \label{fig:dotted_pattern}
	}
%\caption{Simulated Heterogeneous Patterns}
%\label{fig:distance_pdf_simulation_iterative}
%\end{figure}
\end{minipage}
%} & 
\begin{minipage}[c]{0.4\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{table}
%\centering
  \footnotesize
\begin{tabular}{|l|l|l|l|}
\hline
Scene 				& Filter 						& MSE 	& AUC \\
\hline
Point Target 	& f-MLE (incl, 3x3) 	& 1.38	& 0.901 \\
Point Target 	& f-MLE (excl, 3x3) 	& 1.47	& 0.893 \\
Point Target 	& boxcar (3x3) 			& 1.56	& 0.826 \\
Point Target 	& boxcar (5x5) 			& 2.67	& 0.502 \\
\hline
Edge 	& f-MLE (incl, 3x3) 	& 0.68	& 0.969 \\
Edge 	& f-MLE (excl, 3x3) 	& 0.73	& 0.964 \\
Edge 	& boxcar (3x3) 			& 1.03	& 0.942 \\
Edge 	& boxcar (5x5) 			& 1.51	& 0.934 \\
\hline
Line 	& f-MLE (incl, 3x3) 	& 1.89	& 0.791 \\
Line 	& f-MLE (excl, 3x3) 	& 2.02	& 0.767 \\
Line 	& boxcar (3x3) 			& 2.27	& 0.658 \\
Line 	& boxcar (5x5) 			& 2.88	& 0.375 \\
\hline
Dotted 			& f-MLE (incl, 3x3) 	& 2.28	& 0.639 \\
Dotted 			& f-MLE (excl, 3x3) 	& 2.32	& 0.621 \\
Dotted 			& boxcar (3x3) 			& 2.92	& 0.431 \\
Dotted 			& boxcar (5x5) 			& 3.35	& 0.382 \\
\hline
\end{tabular}
%\caption{The MSE \& ROC indices are correlated}
%\end{table}
\end{minipage}
%}
%\end{tabular}
\caption{Heterogeneous Patterns: MSE criteria and f-MLE performance}
\label{fig:Heterogeneous_Patterns}
\end{figure}

@@

The log-transformed domain provides a consistent sense of distance. By embracing
a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes
use of this consistency. Experimental results suggest that the estimatorà¥ˆ output also
exhibits this consistency property, which allows recursive application of the filter discussed above.

@@

\begin{figure}[h]
 \centering
 \epsfxsize=4.8in
 \epsfysize=2.4in
 \epsffile{images/simulation_schema.eps} 	
\caption{SAR simulation, processing and filtering schema}
\label{fig:simul_process_filter_schema}
\end{figure}
%***IVM: Can you make the text bigger, or just increase the figure size? A width of about 12cm would probably be OK.

@@

@@

Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
evaluated by examining the separability of the two background and target populations.
Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
	allows visual evaluation of target and clutter histograms and their separability.
Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
in Figs. \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
respectively, and is measured by computing the Area Under these Curves (AUC).

Detailed examination of Figs. \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
	can help to explain how the MSE is related to the histograms' separation capability.
In pre-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
\ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
Then the separability of background and target populations depends only on the variance of the additive noise. 
This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) of these sample histograms, 
the better the separation capability.

In post-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
\ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
A closer examination of Fig. \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
also introduce bias errors.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are 
always over-estimated. This is probably due to the entropy reduction effect of the speckle filters.
Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.

@@

\begin{table}[h!]
\centering
\begin{tabular}{c|c|c}
Pattern  & AUC - $MSE_{true}$  & AUC - $MSE_{benchmark}$  \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

@@

In the case of partial POLSAR, d=2, then
{\small
\begin{align*}
&  var_2 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1)     = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 &\\
\noindent \text{Similar to the SAR case: } \\
&  1/L + 1/(L-1) < var_2 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) & \\
\noindent \text{Thus, approximately: } \\
& var_2 \left[ \ln |C_v| \right] = 2/(L-1) & \\
\noindent \text{Equivalently: } \\
& L = 2/var_2 \left[ \ln |C_v| \right] + 1 & \\
\end{align*}
}%
%Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
%Thus an approximation can be made: $var_d \left[ \ln |C_v| \right] = 2/(L-1)$.
%Equivalently L can be estimated as:  $L = 2/var_d \left[ \ln |C_v| \right] + 1$

In the case of full POLSAR, d=3, then
{\small
\begin{align*}
&  var_3 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2)    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 & \\
\noindent \text{Again: }  \\
& 1/L + 1/(L-1) + 1/(L-2) < var_3 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3) &\\
\noindent \text{As } L>3 \\
& var_3 \left[ \ln |C_v| \right] = 3/(L-1.5) &\\
\noindent \text{Or: }\\
& L = 3/var_3 \left[ \ln |C_v| \right] + 1.5 &
\end{align*}
}%

%Again, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
%With $L>3$, it is trivial to prove that $3/(L-1.5)$ is also bounded by the same limits. %also is bounded by the above thresholds.
%Thus a similar approximation can be written as: $var_d \left[ \ln |C_v| \right] = 3/(L-1.5)$
%or $L = 3/var_d \left[ \ln |C_v| \right] + 1.5$
